---
title: "Statistical Inference Course Project - Part 2"
author: "Bernardo Najlis"
date: "October 24, 2015"
output: html_document
---

#Introduction

In the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.

* Load the ToothGrowth data and perform some basic exploratory data analyses.
* Provide a basic summary of the data.
* Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
* State your conclusions and the assumptions needed for your conclusions. 

#Load the ToothGrowth data and basic exploratory analysis

```{r}
library(datasets)
data("ToothGrowth")
ToothGrowth$dose <- as.factor(ToothGrowth$dose)

str(ToothGrowth)
nrow(ToothGrowth)
```

#Basic summary of the data

```{r}
summary(ToothGrowth)
table(ToothGrowth$dose, ToothGrowth$supp)

library(ggplot2)
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose))

ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))
```

#Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose

```{r}
```